SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-09-15 README.Rmd
manuscript as github document

* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.
* [The database itself in `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The SylvanSeeds `shiny` app for visualizing the dataset](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* [The report paper describing the collection and fields of the dataset](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md), published in the Journal of Vegetation Science.

>>>>

* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.

### 2020-09-15 doc/manuscript.Rmd
manuscript as github document

---
title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
subtitle: "Running title: SylvanSeeds, a forest germination database"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

>>>>

---
title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
subtitle: "Running title: SylvanSeeds, a forest germination database"
output: github_document
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---
